---
title: "Intergenerational learning with language"
bibliography: [ratchet.bib, library.bib]
csl: apa6.csl
document-params: "10pt, letterpaper"

header-includes: 
  - \usepackage{textcomp}
  
author-information: > 
 \author{{\large \bf Michael Henry Tessler} (mtessler@stanford.edu) \and  {\large \bf Noah D. Goodman} (ngoodman@stanford.edu) \\
         Department of Psychology, Stanford University}

abstract: 
    "The abstract should be one paragraph, indented 1/8 inch on both sides,
in 9 point font with single spacing. The heading Abstract should
be 10 point, bold, centered, with one line space below it. This
one-paragraph abstract section is required only for standard spoken
papers and standard posters (i.e., those presentations that will be
represented by six page papers in the Proceedings)."
    
keywords:
    "Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term."
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

# Proposal

Human understanding exists in the mind but is transmitted within- and across- generations, becoming *cultural knowledge* [@Boyd1985].
Human cultural knowledge seems to accumulate modifications and incremental improvements over time in what is thought of as a "ratchet effect" [@Tomasello1999].
The *cultural ratchet* requires faithful transmission of knowledge from one generation to the next, as well as creative innovation from time to time.
The former, in particular, is important to ensure the ratchet does not "slip", and it is suggested that nonhuman primates struggle with faithful transmission [@Tennie2009].

Faithful transmission is often looked at through the lens of imitation, which is particularly useful for learning procedural knowledge and rituals [e.g., @Legare2015].
Indeed, in pedagogical contexts, human children tend to *overimitate*, reproducing causally unnecessary steps in an action sequence, while nonhuman primates filter these things out [@Horner2005].
But informative demonstrations are only so useful when a teacher's goal is to convey something nonprocedural.
Language, on the other hand, can go beyond the here-and-now and convey information that is abstract, or would be otherwise difficult or unsafe to observe, like learning that a particular plant is poisonous [e.g., @Gelman2009].

Computational models of cultural evolution examine how individual and social learning dynamics evolve over generations [@Boyd1985; @Cavailli1981; @Kalish2007].
It can be shown, for instance, that imitation is a form of free riding, and operating alone can have maladaptive consequences for a population [@Boyd2011].
When the knowledge tranmission process is low-fidelity among individuals, faithful transmissions can still occur at the population level [@Henrich2002].
If agents incidentally pass data intergenerationally, inductive biases (i.e., prior beliefs) can come to dominate the representations in the population [@Griffiths2008].
In terms of the cultural ratchet, inductive biases are bad, drawing agents' beliefs towards what some have described as ``cognitive attractors'' [@Sperber1996] and away from the hard-won knowledge of the innovator.

Bayesian models of cultural transmission have closely examined how information changes as it is passed intergenerationally [@Kalish2007; @Griffiths2008].
@Beppu2009 argue that if what is passed intergenerationally is *beliefs* (i.e., latent representations) and not *data* (i.e., observable behavior), then inductive biases no longer dominate representations and knowledge can be faithfully transmitted across generations (i.e., the cultural ratchet sticks).
There is only one problem with this account: beliefs cannot be passed from one head to the next. 
All a learner has access to from other agents is their observable behavior: actions they take, products they make, or utterances they produce.

# Outline

## Experiments

### Replicate Beppu.

Bugs and trees. 
Different sized bugs lived in  different sized trees.
In the first phase, we will show you a bug and have you guess what sized tree the bug likes.
After each guess, we will show you the right answer. 
In the second phase, again you will see bugs and guess the tree size but this time there will be no feedback.

Could also include a pedagogical demonstration condition.
After the test phase, participants can choose 1, 2, or 4 demonstrations (maybe different conditions).
They get to choose the bug size and then the tree size.

### Extensions

Either a category or causal learning domain, perhaps with hierarchically structured worlds. 
(More towards Nathaniel's worlds.)

## Model

Intergenerational learning with generics.

What is a generic in function learning?
--> "As X increases, Y increases."

The particular setence: "X increased, Y increased."
Semantics for particular: $x_1 - x_0 > 0$ \& $y_1 - y_0 > 0$.

Prior over beta weights (used in the Bayesian regression iterated model) can be refactored into marginal on these diffs.
Representation of the state prior probably should also have other features, like "X decreased, Y increased."
Can then say generics like "As X increases, Y increases." as a vague threshold on that scale.

For this, we may want to start by testing the ratchet (both model and experiment) with a true function of $y = -x$.

For the quadratic functions, we may need to do something compositional in the language: "When X is small, as X increases, Y increases; but when X is large, the opposite."

Otherwise, we will want to develop a comparable model for causal or category learning.

# General Formatting Instructions 

For general information about authoring in markdown, see **[here](http://rmarkdown.rstudio.com/authoring_basics.html).**

For standard spoken papers and standard posters, the entire 
contribution (including figures, references, everything) can be 
no longer than six pages. For abstract posters, the entire contribution 
can be no longer than one page. For symposia, the entire contribution 
can be no longer than two pages.

The text of the paper should be formatted in two columns with an
overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
cm), with 0.25 inches between the columns. Leave two line spaces
between the last author listed and the text of the paper. The left
margin should be 0.75 inches and the top margin should be 1 inch.
\textbf{The right and bottom margins will depend on whether you use
U.S. letter or A4 paper, so you must be sure to measure the width of
the printed text.} Use 10 point Times Roman with 12 point vertical
spacing, unless otherwise specified.

The title should be in 14 point, bold, and centered. The title should
be formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11 point bold, and centered, with the author's
email address in parentheses. Under each author's name list the
author's affiliation and postal address in ordinary 10 point  type.

Indent the first line of each paragraph by 1/8~inch (except for the
first paragraph of a new section). Do not add extra vertical space
between paragraphs.

# First-Level Headings

First level headings should be in 12 point , initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.

## Second-Level Headings

Second level headings should be 11 point , initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~ line
space below the heading.

### Third-Level Headings

Third-level headings should be 10 point , initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

# Formalities, Footnotes, and Floats

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@NewellSimon1972a], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@NewellSimon1972a]. List multiple references alphabetically and
separate them by semicolons [@ChalnickBillman1988a; @NewellSimon1972a]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

For more information on citations in R Markdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.}

## Figures

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```


## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
